\subsection{What to take from this Term Paper}
In the end, what to take from this Term Paper is up to the Reader, however I hope that this Term Paper cleared up that there are no good reasons for War. Even if countries tell us that their War is for the "removal of Nazis" or for the "liberation" of a country, it is never the truth. Every War always boils down to the gain of power or money, although nowadays these things are the same.

The war for Oil results in a shift of power in OPEC, which allows the most powerful country to influence the international Oil price. Due to this easy way of gaining a monopoly, any state can abuse their position in OPEC very easily.

The war against Communism has the goal of defeating an idea that goes against everything the US stands for. Communism tries to abolish the entire concept of a class based society, which would result in the Government any rich people would loose their power. It is clear why the US government tries everything they can to avoid any Communist movement in any country, since they seemingly still believe in the Domino Theory, and fear that any communist country that gains a lot of power could cause other countries to move towards communism.

And finally, the attempts of gaining power in countries. This is not always very easy, as seen with the example of Cuba, getting power over countries can also mean completely blocking any cooperation with specific states, in this case setting an embargo on Cuba and threatening non US companies to sanction them if they decide to trade with Cuba. This gives the US control over every company that is interested in having the US as a partner, which usually every company wants. Based on this example it becomes clear that wars with the objective of directly gaining power in countries does not always mean getting power over the country in which the war is happening, but to gain power over other countries through this war.